Reconstructing the Lensing Mass in the Universe \\ from Photometric Catalogue Data

### 2013-03-04 doc/paper-lcr.tex
small changes

\new{
Throughout this work we have assumed that the universe's halos are populated
with galaxies whose stellar masses are determined purely by the
\citet{BehrooziEtal2010} Stellar Mass--Halo Mass relation, which we then use
in our reconstruction. In practice, the true Stellar Mass--Halo Mass relation
may well be different to the one we assume in our inference, and if it is, 
a systematic error could be incurred.

We investigate the potential size of this systematic error by repeating the
analysis of the previous section, still using the  the
\citet{BehrooziEtal2010} relation to generate the stellar masses of our
calibration lines of sight and hence carry out the inference, but now using
simulated catalog datasets that were generated from the stellar mass--halo
mass relation of \citet{MosterEtal2010}.

@@

TEC thanks Vasily Belokurov for supervision, guidance and suggestions.
We thank Risa Wechsler and Peter Behroozi 
for useful discussions and suggestions.
\input{acknowledgments.tex}

>>>>

\new{

Throughout this work we have assumed that the universe's halos are populated
with galaxies whose stellar masses are determined purely by the
\citet{BehrooziEtal2010} Stellar Mass--Halo Mass relation, which we then use
in our reconstruction. In practice, the true Stellar Mass--Halo Mass relation
may well be different to the one we assume in our inference, and if it is, 
a systematic error could be incurred. It is hard to test the size of this sytematic error, since we do not know how much the real universe differs from the chosen Stellar Mass--Halo Mass relation. As wider and deeper surveys are conducted more data will become available with which to construct the Stellar Mass--Halo Mass relation; this should drive the infered Stellar Mass--Halo Mass relation closer to the truth. We are only interested in testing the effect of changing the Stellar Mass--Halo Mass relation in a way that is consistant with observational constraints; improving the observational contraints on the Stellar Mass--Halo Mass relation will decrease the the potential size of the systematic error on reconstructed $\kappax$ induced by assuming a specfic Stellar Mass--Halo Mass relation.

To estimate the potential size of this systematic error, we repeat the
analysis of the previous section, still using the  the
\citet{BehrooziEtal2010} relation to generate the stellar masses of our
calibration lines of sight and hence carry out the inference, but now using
simulated catalog datasets that were generated from the stellar mass--halo
mass relation of \citet{MosterEtal2010}.

@@

TEC thanks Vasily Belokurov for supervision, guidance and suggestions.
We thank Risa Wechsler and Peter Behroozi 
for useful discussions and suggestions. We are grateful to the referee
for suggesting improvements to the original manuscript.
\input{acknowledgments.tex}
